Species persistence under climate and fishing

### 2014-01-30 Writing/MS.tex
small typos and grammatical edits

There are many stressors that can disturb an ecosystem. Ecologists have quantified the effects of a number of stressors individually \citep{Wilcoveetal1998, Crainetal2008, DarlingCote2008}. However, disturbances rarely occur in isolation and it is therefore important to understand how a system is affected by multiple disturbances together \citep{DoakMorris2010, Fordhametal2013, Foltetal1999}. A perturbation that has little effect when it occurs individually may still amplify the disturbance caused by a coincident perturbation \citep{Crainetal2008, DarlingCote2008}. Synergistic interactions between stressors can be especially problematic if an animal population can persist in the face of a single stressor but the combination of multiple stressors suffices to drive the population extinct (i.e. \citet{Pelletieretal2006}). However it remains difficult to predict when disturbances are likely to interact in ways not anticipated when perturbations are measured individually.

@@

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must 
specify a recruitment function.  Again, we chose to use a Beverton-Holt function.

\noindent where $R_0$ is the intrinsic growth rate and $K$ is the carrying capacity.  In the first generation, we seeded the world with 50 individuals at a single point, as in \citep{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate change by moving the viable patch.

>>>>

There are many stressors that can disturb an ecosystem. Ecologists have quantified the effects of a number of stressors individually \citep{Wilcoveetal1998, Crainetal2008, DarlingCote2008}. However, disturbances rarely occur in isolation, so it is important to understand how a system is affected by multiple disturbances together \citep{DoakMorris2010, Fordhametal2013, Foltetal1999}. A perturbation that has little effect when it occurs individually may still amplify the disturbance caused by a coincident perturbation \citep{Crainetal2008, DarlingCote2008}. Synergistic interactions between stressors can be especially problematic if an animal population can persist in the face of a single stressor but the combination of multiple stressors suffices to drive the population extinct (i.e. \citet{Pelletieretal2006}). However it remains difficult to predict when disturbances are likely to interact in ways not anticipated when perturbations are measured individually.

@@

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must 
specify a recruitment function.  Again, we chose to use a Beverton-Holt function.  In the first generation, we seeded the world with 50 individuals at a single point, as in \citep{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate change by moving the viable patch.
